---
title: "Draw a Rectangle"
teaching: 0
exercises: 0
questions:
- "How do I draw a rectangle?"
objectives:
- "Create rectangles using ggplot2."
- "Set aesthetics (e.g. color, opacity) of drawn object."
keypoints:
- "First key point. Brief Answer to questions. (FIXME)"
---

```{r, include=FALSE}
source("../bin/chunk-options.R")
knitr_fig_path("01-introduction-")
```

```{r load-libraries, echo = FALSE, results='hide', message = FALSE, warning = FALSE}
library(ggplot2)
```

```{r, load-ggplot2, eval = FALSE}
library(ggplot2)
```

```{r, first-rect}
ggplot() + 
  geom_rect(aes(xmin = 1, xmax = 3, ymin = 10, ymax = 15))
```
```{r, add-fill}
ggplot() + 
  geom_rect(aes(xmin = 1, xmax = 3, ymin = 10, ymax = 15), 
            fill = "blue")
```
## Warning
```{r, fill-in-aes}
ggplot() + 
  geom_rect(aes(xmin = 1, xmax = 3, ymin = 10, ymax = 15, fill = "blue"))
```
> ## Your Favorite Color
> 
> ```{r, fav-color}
> ggplot() + 
> geom_rect(aes(xmin = 1, xmax = 3, ymin = 10, ymax = 15), fill = "purple")
> ```
>
{: .challenge}

```{r, add-transparency}
ggplot() + 
  geom_rect(aes(xmin = 1, xmax = 3, ymin = 10, ymax = 15), 
            fill = "blue", alpha = 0.4)
```
Higher alpha is more opaque (less transparent). 

```{r, add-outline}
ggplot() + 
  geom_rect(aes(xmin = 1, xmax = 3, ymin = 10, ymax = 15), 
            fill = "blue", alpha = 0.4, color = "black")
```
```{r, blank-canvas}
ggplot() + 
  geom_rect(aes(xmin = 1, xmax = 3, ymin = 10, ymax = 15), 
            fill = "blue", alpha = 0.4, color = "black") + 
  theme_void()
```

```{r, two-rectangles}
ggplot() + 
  geom_rect(aes(xmin = 1, xmax = 3, ymin = 10, ymax = 15), 
            fill = "blue", alpha = 0.4, color = "black") + 
  geom_rect(aes(xmin = 2, xmax = 5, ymin = 3, ymax = 10), 
            fill = "orange", alpha = 1, color = "black") +
  theme_void()
```
Possible to add each rectangle with a separate line of code (i.e. a separate
call to the `geom_rect()` function), but labor intensive and repetitive.
Instead, we can create a table-like data structure to hold the values we want
to use for each rectangle and iterate through each row of that table with
a single line of code. 

{% include links.md %}



