---
title: "Draw Many Rectangles"
teaching: 0
exercises: 0
questions:
- "How can I draw many rectangles without a lot of code?"
objectives:
- "Create a dataframe to store values (e.g. color) for each rectangle."
keypoints:
- "First key point. Brief Answer to questions. (FIXME)"
---

```{r, include=FALSE}
source("../bin/chunk-options.R")
knitr_fig_path("02-dataframes-")
```

```{r load-libraries, echo = FALSE, results='hide', message = FALSE, warning = FALSE}
library(tidyverse)
```

Figure of dataframe structure from another lesson.

You can make a dataframe by manually entering the values you want to use
for each variable for each rectangle and then bind them together.

```{r dataframe-hard-way}
rect1 <- c(xmin = 1, xmax = 3, ymin = 10, ymax = 15, fill = "blue", alpha = 0.4, color = "black")
rect2 <- c(xmin = 2, xmax = 5, ymin = 3, ymax = 10, fill = "orange", alpha = 1, color = "black")

my_rectangles <- rbind(rect1, rect2)
```

```{r make-df}
my_rectangles <- as.data.frame(my_rectangles)
```

```{r multiple-rectangles-hard-way}
ggplot() + 
  geom_rect(my_rectangles, mapping =  
              aes(xmin = xmin, xmax = xmax, ymin = ymin, 
                  ymax = ymax), 
            fill = my_rectangles$fill, alpha = my_rectangles$alpha, 
            color = my_rectangles$color) + 
  theme_void()
```

This is also really repetitive and annoying if you have many rectangles. 
Instead of specifying all of the variable names, you can do this: 

```{r data-frame-easier}
rect1 <- c(1, 3, 10, 15, "blue", 0.4, "black")
rect2 <- c(2, 5, 3, 10, "orange", 1, "black")

my_rectangles <- rbind(rect1, rect2)
colnames(my_rectangles) <- c("xmin", "xmax", "ymin", "ymax", "fill", "alpha", "color")
```

Note to self: Neither of the above actually creates dataframes, so move intro of dataframe terminology to later. 

> ## Exercise
> Add two more rectangles to your data table.
> 
> ```{r exercise-add-rects}
> rect3 <- c(8, 15, 3, 10, "darkblue", 0.3, "black")
> rect4 <- c(1, 4, 6, 12, "purple", 0.5, "black")
> 
> my_rectangles <- rbind(my_rectangles, rect3, rect4)
> ```
> {: .solution}
{: .challenge}

```{r rects-from-dataframe}
ggplot() + 
    geom_rect(my_rectangles, mapping = 
                aes(xmin = xmin, xmax = xmax, 
                    ymin = ymin, ymax = ymax),
              fill = my_rectangles$fill,
              alpha = my_rectangles$alpha) + 
    theme_void()
```


{% include links.md %}